\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments.text}
\input{../Common.text}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
        
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Feb 12, 2026 & 1.0 & Initial Plan based on Presentation Strategy\\
Mar 03, 2026 & 1.1 & Detailed validation process and systematic reviews added\\
\bottomrule
\end{tabularx}

\newpage

\section{Symbols, Abbreviations, and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule              
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  SRS & Software Requirements Specification\\
  VnV & Verification and Validation\\
  \bottomrule
\end{tabular}\\

\newpage

\pagenumbering{arabic}

This document outlines the Verification and Validation (VnV) plan for the \progname{} system.

\section{General Information}

\subsection{Summary}
\progname{} is a real-time exercise feedback system that uses computer vision (Pose Estimation Library) to estimate pose and a state machine to count repetitions and analyze form. This verification process is critical for the success of this project.

\subsection{Objectives}
The primary objectives of this VnV plan are to:
\begin{itemize}
    \item Build confidence in the correctness of the \textbf{repetition counting logic}.
    \item Verify the \textbf{accuracy} of the biomechanical angle calculations.
\end{itemize}

\subsection{Relevant Documentation}
\citet{SRS} provides the functional and non-functional requirements that will be verified.

\subsection{Scope}
Usability testing is currently out of scope for the Proof of Concept demonstration but will be formally evaluated in future iterations because usability is very important for a consumer-facing mobile application.

\section{Plan}

\subsection{Verification and Validation Team}
The verification team consists of the primary developer (\authname) and the assigned peer reviewers from CAS 741, including Yibing Mei.

\subsection{SRS Verification and Validation}
The SRS has been verified and validated through a systematic plan to ensure the requirements align with both software engineering standards and real-world fitness coaching needs. This plan includes:
\begin{itemize}
    \item \textbf{Scenario-Based Walkthroughs}: Conducting structured reviews with the assigned Domain Expert (Yibing Mei) to trace specific exercise scenarios (e.g., a perfect squat vs. a shallow squat) through the Instance Models, ensuring the biomechanical constraints map to actual coaching expectations.
    \item \textbf{Peer Review}: Asynchronous evaluation by the assigned primary and secondary reviewers from CAS 741 via structured GitHub Issues.
    \item \textbf{Checklist-Based Verification}: Methodical verification of Goal Statements and Input Constraints utilizing the \href{https://github.com/smiths/capTemplate/blob/main/docs/Checklists/SRS-Checklist.pdf}{CAS 741 SRS Checklist}.
\end{itemize}

\subsection{Design Verification}
The Design (MG and MIS) will be verified through:
\begin{itemize}
    \item Peer review (GitHub Issues) by the assigned domain expert and secondary reviewers.
    \item Comparison against the SRS utilizing a Traceability Matrix to ensure all requirements are mapped to corresponding modules.
\end{itemize}

\subsection{Implementation Verification}
Implementation verification will focus on \textbf{Manual Unit Testing} of the core logic and \textbf{Automated Testing} where feasible. Formal reviews will be conducted by the CAS 741 peer reviewers.
\begin{itemize}
    \item \textbf{Static Analysis}: Peer code reviews via GitHub Pull Requests, and automated linting utilizing \texttt{flake8} and \texttt{pylint}.
    \item \textbf{Dynamic Testing}: The primary developer will manually run the system against defined test cases (see Section 4) prior to merging code.
\end{itemize}

\subsection{Automated Testing and Verification Tools}
The following tools will be used:
\begin{itemize}
    \item \href{https://docs.pytest.org/}{\textbf{Pytest}}: Unit and system test execution.
    \item \href{https://github.com/features/actions}{\textbf{GitHub Actions}}: CI — runs linting and automated tests on every push.
    \item \href{https://robotframework.org/}{\textbf{Robot Framework}}: Automated E2E testing for the user interface.
\end{itemize}

\subsection{Software Validation}
\begin{itemize}
    \item \textbf{Dataset}: Validation utilizes a custom recorded dataset consisting of 50 exercise videos. The dataset includes a diverse distribution of correct form, incorrect depth, incorrect angles, varying user heights, and different camera angles to ensure coverage of realistic usage scenarios. Each video has been manually labelled frame-by-frame indicating whether the user is exhibiting correct or incorrect physical form.
    \item \textbf{Validation Approach}: Compare system output against the labelled datasets.
    \item \textbf{Method}: Run \progname{} on the dataset and compare the expected (labelled) outputs against the actual system feedback.
    \item \textbf{Oracle}: The labelled dataset serves as the oracle — it provides the "known truth" for validation.
\end{itemize}

\section{System Tests}

\subsection{Tests for Functional Requirements}

\subsubsection{Repetition Counting (R4)}

\begin{enumerate}
\item{T1: Perfect Squat\\}
Type: Functional, Dynamic, Automated Simulation\\
Initial State: System Initialized\\
Input: Synthetic cosine wave of knee angles ($180^\circ \rightarrow 90^\circ \rightarrow 180^\circ$).\\
Expected Output and Final State: \texttt{RepCount} increments by 1. Final state is Top. State transitions: Top $\rightarrow$ Down $\rightarrow$ Bottom $\rightarrow$ Up $\rightarrow$ Top.\\
Test Case Derivation: Tests the happy path of a full valid repetition.\\
How test will be performed: Automatically feed angle data to the state machine function using pytest.

\item{T2: Failed Rep\\}
Type: Functional, Dynamic, Manual Simulation\\
Initial State: System Initialized\\
Input: Angle dips to $100^\circ$ only (never reaches $90^\circ$ threshold).\\
Expected Output and Final State: \texttt{RepCount} does NOT increment. Feedback: "Go Deeper". Final state is Top.\\
Test Case Derivation: Tests the threshold logic (Boundary Value Analysis).\\
How test will be performed: Manually feed angle data to the state machine function.

\item{T4: State Machine Cycle (IM\_RepetitionCount)\\}
Type: Functional, Dynamic, Manual Simulation\\
Initial State: System Initialized (Bottom State, $p < 0.15$), where $p$ is the normalized scalar progress of the exercise ($0.0 \rightarrow 1.0$).\\
Input: Sequence of $p$ values: $0.1 \rightarrow 0.5 \rightarrow 0.9 \rightarrow 0.5 \rightarrow 0.1$ with $\Delta t = 2.0s$.\\
Expected Output and Final State: \texttt{RepCount} increments by 1. Transitions: Start $\rightarrow$ Ascend $\rightarrow$ Peak $\rightarrow$ Descend $\rightarrow$ Complete. Final State: Complete.\\
Test Case Derivation: Verification of the 5-stage state machine logic.\\
How test will be performed: Feed normalized progress data to the \texttt{analyze\_form} function.

\item{T5: Timing Constraint (Too Fast)\\}
Type: Functional, Dynamic, Manual Simulation\\
Initial State: System Initialized (Top State)\\
Input: Sequence of progress values representing a full rep: $1.0 \rightarrow 0.0 \rightarrow 1.0$. The simulated timestamps for these frames are $t_0 = 0.0s, t_1 = 0.1s, t_2 = 0.2s$ (where $t_{min} = 0.5s$).\\
Expected Output and Final State: \texttt{RepCount} does NOT increment. A warning "Too Fast" is logged. Final State: Top State.\\
Test Case Derivation: Verification of usage constraints defined in IM\_RepetitionCount.\\
How test will be performed: Feed data with fast timestamps directly into the rep counter.

\item{T6: Intermediate State Transition (Ascend)\\}
Type: Functional, Dynamic, Automated Simulation\\
Initial State: Start State ($p = 0.1$)\\
Input: Normalized progress increases to $p = 0.6$.\\
Expected Output and Final State: The state machine transitions to the Ascend state. \texttt{RepCount} does not increment.\\
Test Case Derivation: Verification that the intermediate ascending threshold triggers correctly.\\
How test will be performed: Automatically pass $p$ values into the state machine and assert the returned state Enum.

\item{T7: State Reversal (Failed Transition)\\}
Type: Functional, Dynamic, Automated Simulation\\
Initial State: Ascend State ($p = 0.6$)\\
Input: Normalized progress decreases back to $p = 0.1$ instead of continuing to Peak.\\
Expected Output and Final State: The state machine transitions back to the Start state. \texttt{RepCount} does not increment.\\
Test Case Derivation: Verification that the state machine handles reversals and does not erroneously count incomplete movements.\\
How test will be performed: Automatically pass $p$ values into the state machine and assert the returned state Enum.
\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

\subsubsection{Accuracy (NFR1)}

\begin{enumerate}
\item{T8: Geometric Verification (Static Dataset)\\}
Type: Functional/Non-Functional, Dynamic, Automated\\
Initial State: System Initialized\\
Input: A dataset of 20 static images with known, labeled joint angles (measured physically with a goniometer).\\
Expected Output and Final State: Calculated angles for all 20 images correspond to the labeled ground truth. System logs an average error delta.\\
Test Case Derivation: Verification of the core measurement engine accuracy via a posteriori measurement.\\
How test will be performed: Run the extraction module chronologically across the labeled static dataset and compute the mean absolute error.

\item{T9: Dynamic Occlusion Verification (Video Dataset)\\}
Type: Non-Functional, Dynamic, Automated\\
Initial State: System Initialized\\
Input: A labeled video dataset containing 10 scenarios where the subject is temporarily occluded by an object.\\
Expected Output and Final State: The system successfully identifies the frames as occluded (via low confidence scores) and gracefully ignores those frames for angle extraction without crashing.\\
Test Case Derivation: Verification of robustness and accuracy in imperfect environments.\\
How test will be performed: Automated script processes the occluded videos and asserts the error handling flow.
\end{enumerate}

\section{Traceability Matrices}
Table~\ref{Table:trace} shows the traceability between the requirements from the SRS and the system tests outlined in this document.

\begin{table}[h!]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Requirement} & \textbf{Test Cases} \\
\hline
R1 & T4, T5, T6, T7, T9 \\
R2 & T8, T9 \\
R3 & T8, T9 \\
R4 & T1, T2 \\
R5 & T1, T2, T4 \\
\hline
\end{tabular}
\caption{Traceability Matrix: Requirements to Tests}
\label{Table:trace}
\end{table}

\section{Unit Test Description}

\subsection{Unit Testing Scope}
Unit testing will focus on the \textbf{Analysis Module} (State Machine), as it contains the critical business logic. The UI, video input stream, and end-to-end user feedback loops will not be covered by automated unit tests due to the difficulty of mocking the camera context reliably, and are instead verified via dynamic simulation testing.

\subsection{Tests for Functional Requirements}
The tests T1, T6, and T7 defined in the System Tests section also serve as the primary Unit Tests for the Analysis Module.

\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\newpage

\section{Appendix}
N/A

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.

\input{../Reflection.text}

\begin{enumerate}
  \item What went well? Planning the "Manual Unit Tests" helped clarify the logic before writing code.
  \item Pain points? Determining how to verify accuracy without an expensive motion capture system. Resolved by using static goniometer measurements.
  \item Skills needed? Knowledge of Python `pytest` for future automation and Pose Estimation constraints.
\end{enumerate}

\end{document}